SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-01-18 scipy-1.0/paper.tex
Substantiate competition resources in intro

SciPy's arrival at this point is surprising, and somewhat anomalous.
When started, the library had little funding, and was written mainly
by graduate students---many of them without a computer science education, and often without the
blessing of their advisors.  To even imagine that a small group of
``rogue'' student programmers could upend the already well-established
ecosystem of research software---backed by millions in funding, and
thousands of highly qualified engineers---was preposterous.

@@

By the middle to late 2000s, SciPy was starting to mature after a long phase of significant
growth and adoption.
The informal workshops grew into international conferences with many
hundreds of attendees. Special issues were organized and published in a
leading scientific journal, and the scope of the SciPy library
narrowed, while the breadth of the ecosystem grew
through a new type of auxiliary package, the scikit.  The tooling,
development, and release processes became more professional, grown with
the patience affordable in open source development. Leading with
best practices nowadays is increasingly common in both industry and other
open source projects \cite{millman2014developing}.

@@

In the early workshops, recurrent topics indicate the state of development, with
emphasis being placed on the underlying array package, plotting,
parallel processing, acceleration / wrapping, and user interfaces.  By
2004, a significant shift occurred towards application of SciPy to
scientific problems.  The event also started to draw in more keynote
speakers from outside the community, such as Guido van Rossum (creator
of Python, 2006), Ivan Krstić (One Laptop per Child, 2007), Alex
Martelli (Google, 2008), and Peter Norvig (Google Research, 2009).
The SciPy conference went from being a small gathering of
core developers, to a multi-location event, with increased funding, a
published proceedings, and scholarships for attending students (some
of whom are authors on this paper).  In 2010, the conference grew even
further, with an additional event added in India, and the US
conference—now with parallel tracks—moving to Austin, Texas.
While the US SciPy conference kept growing (by ... it had multiple
tracks, student sponsorship, proceedings, and funding), satellite
events were being organized by volunteers elsewhere, such as EuroSciPy
(2008–) and SciPy India (2009–).
Special sessions and minisymposia dedicated to scientific Python began
appearing at many events.
For example, a three-part minisymposium organized for CSE 2009 was
featured in SIAM News\cite{siamcse09}.

>>>>

SciPy's arrival at this point is surprising, and somewhat anomalous.
When started, the library had little funding, and was written mainly
by graduate students---many of them without a computer science education, and often without the
blessing of their advisors.  To even imagine that a small group of
``rogue'' student programmers could upend the already well-established
ecosystem of research software---backed by millions in funding, and
thousands of highly qualified engineers\cite{mathworks-globe-97,
esri-revenue}---was preposterous.

@@

By the middle to late 2000s, SciPy was starting to mature after a long phase of significant
growth and adoption.
The informal workshops grew into international conferences with many
hundreds of attendees. Special issues were organized and published in a
leading scientific journal\cite{dubois2007guest}, and the scope of the SciPy library
narrowed, while the breadth of the ecosystem grew
through a new type of auxiliary package, the scikit\cite{scikits-general}. 
The tooling, development, and release processes became more professional.
SciPy was expanded carefully, with the patience affordable in open source 
projects and via best practices common in industry \cite{millman2014developing}.

@@

In the early workshops, recurrent topics reflected the state of development, with
emphasis being placed on the underlying array package, plotting,
parallel processing, acceleration / wrapping, and user interfaces.  By
2004, a significant shift occurred towards application of SciPy to
scientific problems.  The event also started to draw in more keynote
speakers from outside the community, such as Guido van Rossum (creator
of Python, 2006), Ivan Krstić (One Laptop per Child, 2007), Alex
Martelli (Google, 2008), and Peter Norvig (Google Research, 2009).
The SciPy conference went from being a small gathering of
core developers, to a multi-location event, with increased funding, a
published proceedings, and scholarships for attending students (some
of whom are authors on this paper).  In 2010, the conference grew even
further, with an additional event added in India, and the US
conference—now with parallel tracks—moving to Austin, Texas.
While the US SciPy conference kept growing (by ... it had multiple
tracks, student sponsorship, proceedings, and funding), satellite
events were being organized by volunteers elsewhere, such as EuroSciPy
(2008–) and SciPy India (2009–).
Special sessions and minisymposia dedicated to scientific Python began
appearing at many events.
For example, a three-part minisymposium organized for CSE 2009 was
featured in SIAM News\cite{siamcse09}.
